Schema Change: Challenge Problems

### 2024-05-16 paper.tex
OK it's two paragraphs

@@

\textcolor{red}{[TVDS] Super rough attempt at the paragraph:}

>>>>

\section{\textcolor{red}{[TVDS] Super rough attempt at the paragraph}}

\section{\textcolor{red}{[JE] Type evolution for live programming}}

Many past improvements in the practice of programming worked by speeding up feedback loops. Live Programming aspires to the optimum of immediate feedback. The problem is that modern software is built out of many layers of different technologies -- thoroughly live programming would propagate changes immediately up and down the entire stack of a running system, from the database to the code, and from the client to the server. We call this \textit{full-stack} live programming. Another problem is that modern software is built with complex collaborations involving development, testing, deployment, and suppport. Such workflows are themselves feedback loops -- throughly live programming would propagate changes between participants frictionlessly. We call this \textit{end-to-end} live programming.

We propose a research agenda towards this greater vision of live programming. The starting point is database \textit{schema evolution}, which propagates database schema changes into data migrations and query rewriting. We call for generalized \textit{type evolution} that works immediately across the entire software stack, and automatically across the entire software workflow. This paper contributes a set of challenge problems to serve as targets for research on type evolution and as a basis of comparison for the results.

@@
